\section{Related work}\label{sec:related-work}

\gls{nlp} algorithms have been integrated into robotics systems for a myriad of applications, ranging from control of industrial robotic arms \cite{Akan2011,Watanabe2006} and mobile robots \cite{Matuszek2013} to complex interaction with humanoid systems using a combination of voice, text and image perception analysis \cite{Neo2008,Barabas2012}. For the voice and textual teaching, the objects names and relations can be identified using \gls{ner} algorithms \cite{Leon2014,Dlugolinsky2013}. This type of approach usually relies on syntactic and semantic parsing of the text and also in machine learning algorithms \cite{Ekbal2012} in order to be able to recognize previously unseen object names. It may present some challenges \cite{Ratinov2009}, but it can achieve multilingual entity recognition \cite{Rami2014} if language agnostic attributes are used.

Advanced applications of \gls{nlp} algorithms include the teaching of assembly operations to robot arm manipulation systems by human operators. The JAST robot presented in \cite{Rickert2007} was implemented using a multi agent system capable of learning assembly operations by interpreting human voice commands along with their gestures and gaze. The speech recognition system uses a \gls{ccg} and a semantics module to analyze if the operator is making statements for teaching, asking for information or giving answers to previous questions made by the robot. The vision system besides tracking the hands and gaze of the operator to perform a better speech analysis, it also recognizes the assembly objects within the robot workspace using template matching techniques.

Another example of usage of \gls{nlp} methods in an industrial scenario is presented in \cite{Stenmark2013}, in which it is used a multi-lingual statistical semantic parser to extract assembly operations from natural language sentences given by remote operators. The system was developed using a client-server architecture, containing a natural language parser, a \gls{kif} and an engineering system. The parser finds predicates with their respective arguments in sentences and establishes coreference chains. The \gls{kif} contains ontologies and semantically annotated skills that are used for filtering the predicates and return only the ones relevant for assembly operations. Lastly, the engineering system is a high level program interface that uses the predicates found by the parser to select the appropriate skills for assembly while also matching the predicates arguments with the knowledge database in order to identify the objects and analyze in which branch of the assembly tree they must be inserted for achieving proper assembly order.

Besides voice and textual input from humans, the assembly information can also be retrieved from online web pages or knowledge repositories. The system proposed in \cite{Tenorth2010} can extract the assembly graph by performing a syntactic and semantic analysis using a \gls{pcfg} parser and a \gls{pos} tagger followed by word sense retrieval and disambiguation using the WordNet database and the Cyc ontology. After having a preliminary assembly plan, it is executed in simulation to perform a high level validation and also to allow the optimization of the robot movements. If ambiguous or missing information is detected, the system tries to generate a valid assembly plan by analyzing the objects' environment, assembly context and also similar operations stored in its knowledge base.

Several datasets for \gls{ner} have been presented over the years for news and tweets \cite{Dojchinovski2013,Roder2014}. This paper aims to provide a dataset for evaluating \gls{ner} systems with a corpus containing a diverse range of assembly operations for small complex objects (alternators, gearboxes and engines).
